Colonies - Compute Continuums across Platforms

### 2023-04-14 paper_2023/paper.tex
wip

The primary objective of the Colonies framework is to offer uninterrupted access to computing resources, without interruptions or limitations, allowing data to flow from one service to another. To establish such seamless compute continuums, the paper introduces Colonies, a \emph{decentralized runtime environment} designed to easily integrate with third-party systems to create a seamlessly integrated computing ecosystem. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where workflows can be decomposed into independent microservices that can easily be integrated with other systems or applications running anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems across platforms.

@@

\subsection{Earth Observation}
OpenEO \cite{openeo} is an open-source project that aims at providing a standardized and interoperable solution for accessing, processing, and analyzing Earth observation (EO) data. Its primary objective is to facilitate seamless user interaction with diverse data sources and processing backends through a unified API. An overview of various OpenEO backends is presented in \cite{openeo_backends}. The paper concludes that there is a need for a more decentralized and federated EO data processing platform, and OpenEO represents a significant step in this direction. Nevertheless, the paper also acknowledges that the implementation of underlying datacubes, storage solutions, and service plans cannot be entirely abstract away by the OpenEO API.

>>>>

The long-term vision of the Colonies framework is to offer uninterrupted access to computing resources, without interruptions or limitations, allowing data to flow from one service to another. To establish such seamless compute continuums, the paper introduces Colonies, a \emph{decentralized runtime environment} designed to easily integrate with third-party systems to create a seamlessly integrated computing ecosystem. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where workflows can be decomposed into independent microservices that can easily be integrated with other systems or applications running anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems across platforms.

@@

% \subsection{Earth Observation}
% OpenEO \cite{openeo} is an open-source project that aims at providing a standardized and interoperable solution for accessing, processing, and analyzing Earth observation (EO) data. Its primary objective is to facilitate seamless user interaction with diverse data sources and processing backends through a unified API. An overview of various OpenEO backends is presented in \cite{openeo_backends}. The paper concludes that there is a need for a more decentralized and federated EO data processing platform, and OpenEO represents a significant step in this direction. Nevertheless, the paper also acknowledges that the implementation of underlying datacubes, storage solutions, and service plans cannot be entirely abstract away by the OpenEO API.
